Promotors' reports on the first draft of the thesis document.

### 2020-08-21 Extras/ListofPublications.tex
Story 182: Intro complete
Second review version
Final version before internal defense
Second draft before public defense

\subsubsection*{Journal publication2}

\noindent G. Quintana-Carapia, I. Markovsky, R. Pintelon, P. Z. Csurcsia and D. Verbeke, "Experimental validation of a data-driven step input estimation method for dynamic measurements," \textit{IEEE Transactions on Instrumentation and Measurement}, Vol. x, No. x, pp. xx-xx, 2019, doi: 10.1109/TIM.2019.2951865

\vspace{0.2cm}

@@

\vspace{0.2cm}
\noindent G. Quintana-Carapia, I. Markovsky, "Input parameters estimation from time-varying measurements," \textit{Measurement}, Vol. 153, No. 1, pp. 107418, 2020, ISSN 0263-2241, doi: 10.1016/j.measurement.2019.107418.

\vspace{0.2cm}
\subsubsection*{Conference publications}

@@

\vspace{0.2cm}

>>>>

\subsubsection*{Journal publications}

@@

%\vspace{0.1618cm}

\noindent G. Quintana-Carapia, I. Markovsky, R. Pintelon, P. Z. Csurcsia and D. Verbeke, "Experimental validation of a data-driven step input estimation method for dynamic measurements," \textit{IEEE Transactions on Instrumentation and Measurement}, \color{blue} vol. 69, no. 7, pp. 4843-4851, July 2020, \color{black} doi: 10.1109/TIM.2019.2951865.

%\vspace{0.1618cm}

\noindent G. Quintana-Carapia, I. Markovsky, "Input parameters estimation from time-varying measurements," \textit{Measurement}, Vol. 153, No. 1, pp. 107418, 2020, ISSN 0263-2241, doi: 10.1016/j.measurement.2019.107418.

\vspace{0.1618cm}
\subsubsection*{Conference publications}

@@

%\vspace{0.1618cm}
